\documentclass[10pt]{article}
\usepackage[T1]{fontenc}
\usepackage[hidelinks]{hyperref}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage[expansion=false]{microtype}

\geometry{a4paper, top=12mm, bottom=12mm, left=16mm, right=16mm}

% ── Palette ──────────────────────────────────────────────────────────────────
\definecolor{accent}{RGB}{15,75,155}
\definecolor{muted}{RGB}{100,100,100}
\definecolor{light}{RGB}{240,245,255}

% ── Hyperlinks ────────────────────────────────────────────────────────────────
\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

% ── List compression ──────────────────────────────────────────────────────────
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\renewcommand{\labelitemi}{\textcolor{accent}{\textbullet}}
\newenvironment{cvlist}{%
  \begin{itemize}%
  \setlength{\itemsep}{1pt}%
  \setlength{\topsep}{2pt}%
  \setlength{\parsep}{0pt}%
  \setlength{\leftmargin}{1.3em}%
  \small%
}{%
  \end{itemize}%
}

% ── Section heading ───────────────────────────────────────────────────────────
\newcommand{\cvsection}[1]{%
  \vspace{9pt}%
  {\color{accent}\bfseries\large #1}%
  \par\nobreak\vspace{-4pt}%
  {\color{accent}\rule{\linewidth}{0.7pt}}%
  \vspace{4pt}%
}

% ── Job entry ─────────────────────────────────────────────────────────────────
\newcommand{\job}[3]{%
  \textbf{#1} — \textit{#2}\hfill{\small\color{muted}#3}%
  \par\vspace{1pt}%
}

% ── Profile summary box ───────────────────────────────────────────────────────
\newcommand{\profilebox}[1]{%
  \vspace{2pt}%
  \noindent\colorbox{light}{%
    \parbox{\dimexpr\linewidth-2\fboxsep\relax}{%
      \vspace{5pt}\small #1\vspace{5pt}%
    }%
  }%
  \vspace{2pt}%
}

% ── Skill category row ────────────────────────────────────────────────────────
\newcommand{\skillrow}[2]{%
  \textcolor{accent}{\small\textbf{#1}}\enspace\textcolor{muted}{\small|}\enspace{\small #2}\\[2pt]%
}

\begin{document}
\pagestyle{empty}

% ── Header ───────────────────────────────────────────────────────────────────
\begin{center}
  {\fontsize{26}{30}\selectfont\textbf{Sergei Chudov}}\\[4pt]
  {\large\color{muted}Lead / Senior Software Engineer}\\[6pt]
  \small
  \href{mailto:chudov42@gmail.com}{chudov42@gmail.com}\enspace\textcolor{muted}{·}\enspace
  \href{https://linkedin.com/in/window-generator}{linkedin}\enspace\textcolor{muted}{·}\enspace
  \href{https://github.com/WindowGenerator}{github}\enspace\textcolor{muted}{·}\enspace
  \href{https://t.me/WidowGenerator}{telegram}\enspace\textcolor{muted}{·}\enspace
  +374\,91\,186\,658\enspace\textcolor{muted}{·}\enspace
  Yerevan, Armenia
\end{center}

{\color{accent}\rule{\linewidth}{1.2pt}}
\vspace{2pt}

\profilebox{Senior/Lead engineer with \textbf{6 years} of experience building production services,
infrastructure tooling, and bioinformatics pipelines.
Strong Python and Kubernetes background. Track record of owning incidents end-to-end,
shipping internal SDKs, and driving team-wide engineering standards.
Open to relocation or remote.}

% ── Experience ───────────────────────────────────────────────────────────────
\cvsection{Experience}

\job{Lead / Senior Software Engineer}{Bostongene, Yerevan}{Jun 2022 – Present}
\begin{cvlist}
  \item Owned production services (FastAPI, Airflow, pipelines) in Kubernetes; led incident response across \textbf{200+ production issues} and capacity planning.
  \item Wrote \href{https://github.com/WindowGenerator/netfs_unlker}{\texttt{netfs\_unlker}} (Rust) to recover a locked NetApp DB — saved \textbf{2 weeks of work} across multiple teams.
  \item Delivered a patient-parameter DSL library with tests and CI/CD in \textbf{4 days}.
  \item Led end-to-end design and delivery of a policy-annotation billing service (requirements → architecture → production).
  \item Introduced team-wide linting, formatting, and test standards — reduced review friction and bug rate.
  \item Migrated on-prem storage (ONTAP) to AWS EBS and replaced static AWS credentials with IRSA roles — reduced cloud storage costs and eliminated credential exposure risk for a regulated medical data platform.
  \item Shipped an internal Python SDK for genomic cohort data access adopted by data science teams, enabling analyst self-service and reducing ad-hoc engineering support.
  \item \textbf{Stack:} Python · FastAPI · SQLAlchemy · asyncio · Airflow · TypeScript · React · Redux · Docker · Kubernetes · Helm · Concourse · GitLab CI · Vault · PostgreSQL · Neo4j · Redis · RabbitMQ · Kafka
\end{cvlist}

\vspace{4pt}
\job{Middle Software Engineer}{USSC Ltd., Yekaterinburg}{Oct 2019 – Mar 2022}
\begin{cvlist}
  \item Built a system for detecting and preventing security incidents in ICS/industrial networks.
  \item Rewrote master-master replication module with full test coverage, eliminating a class of recurring outages.
  \item Created an OpenAPI→TypeScript client generator; reduced bundle memory and improved API ergonomics.
  \item Built MySQL/Postgres backup service and Elasticsearch index-rotation tooling.
  \item \textbf{Stack:} Python · FastAPI · aiohttp · Flask · SQLAlchemy · TypeScript · Angular · Docker · Jenkins · PostgreSQL · MySQL · Elasticsearch · RabbitMQ
\end{cvlist}

\vspace{4pt}
\job{Trainee ML Engineer}{NPO Avtomatiki, Yekaterinburg}{Mar 2019 – May 2019}
\begin{cvlist}
  \item Prototyped real-time face identification from CCTV using YOLOv3; optimised inference on low-power hardware.
  \item \textbf{Stack:} Python · TensorFlow · Keras · scikit-learn
\end{cvlist}

% ── Skills ───────────────────────────────────────────────────────────────────
\cvsection{Skills}
\skillrow{Backend}{Python · FastAPI · asyncio · SQLAlchemy · golang}
\skillrow{Infrastructure}{Docker · Kubernetes · Helm · Linux · CI/CD (Concourse, GitLab CI, Jenkins)}
\skillrow{Frontend}{TypeScript · React · Angular}
\skillrow{Data}{PostgreSQL · MySQL · Redis · RabbitMQ · Kafka · Elasticsearch · Neo4j}

% ── Open Source & Projects ───────────────────────────────────────────────────
\cvsection{Open Source \& Projects}
\begin{cvlist}
  \item Contributions: \href{https://github.com/mosquito/aio-pika}{\texttt{aio-pika}} \textcolor{muted}{·} \href{https://github.com/astral-sh/ruff}{\texttt{ruff}} \textcolor{muted}{·} \href{https://github.com/langchain-ai/chat-langchain}{\texttt{chat-langchain}}
  \item \href{https://github.com/WindowGenerator/starlette-responses-kit}{\texttt{starlette-responses-kit}} — custom Starlette response types
  \item \href{https://github.com/WindowGenerator/netfs_unlker}{\texttt{netfs\_unlker}} — Rust CLI to unlock \texttt{fcntl} shared locks on NetApp volumes
\end{cvlist}

% ── Education & Languages ────────────────────────────────────────────────────
\cvsection{Education \& Languages}
\textbf{Ural State Technical University} — B.Eng. Design \& Technology of Electronic Facilities
\hfill{\small\color{muted}2015 – 2020}\\
\small
Coursera: \href{https://www.coursera.org/learn/algorithms-part1}{Algorithms Part I} (2020)
\textcolor{muted}{·}
\href{https://www.coursera.org/learn/vvedenie-mashinnoe-obuchenie}{Intro to Machine Learning} (2021)

\vspace{4pt}
Russian — native \quad\textcolor{muted}{|}\quad English — B1

\end{document}
